\documentclass[11pt,a4paper]{article}

\usepackage[margin=0.75in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{array}

\setlength{\parindent}{0pt}
\setlength{\parskip}{1.5pt}
\renewcommand{\arraystretch}{1.08}
\setlist[itemize]{leftmargin=1.2em, itemsep=1pt, topsep=1pt, parsep=0pt, partopsep=0pt}
\titleformat{\section}{\normalsize\bfseries\MakeUppercase}{\thesection}{0em}{}
\titlespacing*{\section}{0pt}{8pt}{3pt}

\newcommand{\resumeSubheading}[4]{
  \textbf{#1} \hfill #2\\
  \textit{#3} \hfill \textit{#4}
}

\begin{document}

{\LARGE \textbf{MUSKAN KUMARI}}\\[4pt]

\section*{Academic Details}
\begin{tabular}{>{\bfseries}p{0.17\linewidth} p{0.31\linewidth} p{0.34\linewidth} p{0.14\linewidth}}
Year & Degree / Board & Institute & GPA / Marks \\
\hline
--- & B.Tech in Mechanical Engineering & Indian Institute of Technology Delhi & 7.13 \\
2021 & CBSE & S.R. Century School & 96.6\% \\
2019 & HBSE & Sports Sainik Public School & 9.40 \\
\end{tabular}

\section*{Scholastic Achievements}
\begin{itemize}
  \item ETH-Global Singapore Hackathon: ZK-Market won the Rootstock track for the best project award (2024).
  \item ETH-Mumbai Hackathon: Won the main track in Zero Knowledge, Best project award out of 15,000 participants (2024).
  \item JEE Advanced Rank: AIR 1147 (GE), AIR 8928 among 0.2 million qualified candidates (2022).
  \item JEE Mains Score: 98.3 percentile among more than 1.1 million candidates (2022).
  \item Certified participant in Cryptography Summer School, covering ZK proofs, SNARKs, MPC, FHE, and blockchain (2025).
\end{itemize}

\section*{Internship}
\resumeSubheading{Encifher}{May 2025 -- July 2025}{Cryptography Research Engineer}{}
\begin{itemize}
  \item Designed a Rust-based Key Management System (KMS) using threshold ElGamal encryption.
  \item Implemented relaxed discrete log DKG and Pedersen Verifiable Secret Sharing for trustless key management.
  \item Implemented a Bulletproof protocol tailored for Solana for efficient zero-knowledge range proofs.
  \item Worked with elliptic curve accumulators to build privacy-preserving integrity checks with verifiable state consistency.
  \item Led research and implementation of encryption schemes including ECIES and ElGamal.
\end{itemize}

\section*{Projects}
\resumeSubheading{BrainfuckVM | ETH-India 2024}{Nov 2024 -- Dec 2024}{}{}
\begin{itemize}
  \item Designed and implemented prover and verifier for a BrainSTARK zero-knowledge virtual machine in Rust.
  \item Built foundational ZKVM libraries, including a custom implementation of FRI.
  \item Built supporting crates from scratch for secure systems programming and cryptographic protocols.
\end{itemize}

\resumeSubheading{Zk-Market | ETH-Global Singapore 2024}{Sep 2024 -- Oct 2024}{}{}
\begin{itemize}
  \item Built a marketplace bridging Web2 and Web3 using zero-knowledge proofs.
  \item Leveraged ZK-TLS to establish secure connections with Web3 networks for privacy and trustless verification.
  \item Enabled on-chain verification of Web2 data using proxy-based ZK-TLS with Reclaim Protocol.
  \item Facilitated seamless Web2-to-Web3 data transfer for secure marketplace interactions.
\end{itemize}

\resumeSubheading{Zero-Knowledge Compiler | ETH-Mumbai 2024}{Mar 2024 -- Apr 2024}{}{}
\begin{itemize}
  \item Worked from the paper \textit{CirC: Compiler infrastructure for proof systems, software verification, and more}.
  \item Developed a compiler for generating and verifying proofs of high-level language computations.
  \item Implemented support for C, Rust, Python, Solidity, and ZoKrates, compiling to R1CS (Groth16).
  \item Designed an extensible backend to support cryptosystems including FHE and MPC.
\end{itemize}

\resumeSubheading{Quark Layer | BlocSoc R\&D}{Apr 2024 -- Mar 2025}{}{}
\begin{itemize}
  \item Built a decentralized proof verification and aggregation layer for zero-knowledge proofs.
  \item Provided near-instant soft crypto-economic guarantees and delayed cryptographic guarantees.
  \item Added support for Succinctlabs SP1, RISC Zero zkVM, Polygon Miden, and Jolt for interoperability.
\end{itemize}

\resumeSubheading{Zkin.gen | ETH-India Hackathon 2023}{Nov 2023 -- Dec 2023}{}{}
\begin{itemize}
  \item Built a decentralized platform for ownership and control of genetic data.
  \item Improved privacy and addressed concerns of centralized genetic-testing platforms.
\end{itemize}

\section*{Technical Skills}
\begin{itemize}
  \item \textbf{Programming Languages \& Tools:} Java, Python, Solidity, Rust, Autodesk Inventor, SolidWorks, MS Office.
  \item \textbf{Libraries:} TensorFlow, PyTorch, Scikit-learn, Pandas, NumPy, Circom, Matplotlib, Graphviz, XGBoost.
  \item \textbf{Web3 Development \& Frameworks:} EVM, Hardhat, Ethers, Web3.js, Foundry (Solidity), EIPs, NFT and ERC20 standards, dApp infrastructure.
  \item \textbf{Zero Knowledge:} Hands-on with Groth16 and FRI protocol implementations.
\end{itemize}

\section*{Positions of Responsibility}
\begin{itemize}
  \item Overall Coordinator, Blockchain Society, IIT Delhi: Leading a team of 25+ members and overseeing research (Apr 2025 -- Present).
  \item Coordinator, Blockchain Society, IIT Delhi: Led research initiatives/projects and organized workshops (Apr 2024 -- Mar 2025).
  \item Executive, Blockchain Society, IIT Delhi: Organized and led workshops on blockchain fundamentals (Jun 2023 -- May 2024).
  \item Vice Captain (Football), Himadri, BHM: Led inter-hostel squad, coordinated training, and fostered team spirit (Jun 2023 -- May 2024).
\end{itemize}

\section*{Additional IIT Information}
\begin{itemize}
  \item Degree: B.Tech in Mechanical Engineering, IIT Delhi; CGPA 7.13; Department Rank 47.
  \item Qualifying Exam: JEE Advanced Rank 1147 (GE).
  \item Key coursework: Intro to Electrical Engineering, Calculus, Electromagnetic Waves \& Quantum Mechanics, Intro to Computer Science, Professional Ethics \& Social Responsibility, Language \& Writing Skills, Engineering Visualization \& Communication, Linear Algebra \& Differential Equations, Intro to Statistics, Data Structures and Algorithms, Mechanical Engineering Drawing.
\end{itemize}

\end{document}
